Experimentally Informed Site-Specific Substitution Models Substantially Deepen Viral Divergence Estimates

### 2018-01-18 manuscript/manuscript.tex
outlined the third results section

>>>>

\begin{itemize}
\item To test the effect of substitution model on data with site-specific amino acid frequencies, we simulated sequences under an ExpCM and re-inferred the branch lengths using different substitution models.
\item Uniform stationary state models underestimate long branches
\begin{itemize}
\item GY94 and GY94 + $\Gamma\omega$ both underestimate long branches 
\item The \textit{averaged} ExpCMs also underestimate long branches. These control models have uniform stationary states but still derive some information from the experiments. 
\item Non-uniform stationary state models accurately estimate long branches
\end{itemize}
\item If sequences have site-specific amino acid frequencies then non-uniform stationary state models, even with $\Gamma\omega$, will underestimate long branches.
\end{itemize}
